---
title: ""
date: "`r format(Sys.time(), '%Y-%m-%d')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Data Description
- Background: 簡述資料內容。若是新接收到的資料，請說明為何會收到這份資料，要分析什麼。
- date received: YYYYMMDD
- Path to data file: 原始資料在資料中心（如行資）之路徑。請填寫原始檔案之路徑。
- Unit of observation:
- Sample period:
- Known issues:
    -
    -
- Definition for each variable:
    -
    -
- Data path: `data/raw/<INPUT_FILE_NAME.csv>` (exact local project-relative file, separate from the source location above)
- Role: `raw`
- Verification status: `<pending; record the actual read/check results after execution>`
- SHA-256: `<pending; fill from the actual file, not a copied example>`
- Next processing notebook: `data/code/<PROCESSING_NAME.ipynb-or-Rmd>` (pending until created)

This notebook documents the unchanged raw file. It does not clean or overwrite it.
Paths below resolve from the project root or from `data/raw/`, `data/code/`, and
`data/processed/`. Replace all placeholders and choose reader options for the
actual format, encoding, IDs, dates, and missing-value codes before execution.

```{r}
library(readr)

find_project_root <- function(start = getwd()) {
  candidate <- normalizePath(start, winslash = "/", mustWork = TRUE)
  repeat {
    if (file.exists(file.path(candidate, "AGENTS.md")) &&
        dir.exists(file.path(candidate, "templates"))) return(candidate)
    parent <- dirname(candidate)
    if (identical(parent, candidate)) stop("Open this notebook within the student project containing AGENTS.md and templates/.")
    candidate <- parent
  }
}
PROJECT_ROOT <- find_project_root()

project_file <- function(relative_path, area, must_exist = TRUE) {
  # Exact project-relative paths only; no first-file search or OS-root /data path.
  parts <- strsplit(relative_path, "/", fixed = TRUE)[[1]]
  if (grepl("^(/|~|[A-Za-z]:)", relative_path) || ".." %in% parts ||
      grepl("<", relative_path, fixed = TRUE) ||
      !startsWith(relative_path, paste0("data/", area, "/"))) {
    stop("Replace the placeholder with an exact path inside data/", area, "/: ", relative_path)
  }
  path <- file.path(PROJECT_ROOT, relative_path)
  if (must_exist && (!file.exists(path) || dir.exists(path))) stop("Input file not found: ", path)
  # Resolve existing ancestors to reject a path that leaves the project via a symlink.
  ancestor <- path
  while (!file.exists(ancestor)) ancestor <- dirname(ancestor)
  resolved <- normalizePath(ancestor, winslash = "/", mustWork = TRUE)
  allowed <- normalizePath(file.path(PROJECT_ROOT, "data", area), winslash = "/", mustWork = TRUE)
  if (!startsWith(allowed, paste0(PROJECT_ROOT, "/"))) {
    stop("data/", area, "/ resolves outside the project root.")
  }
  if (!identical(resolved, allowed) && !startsWith(resolved, paste0(allowed, "/"))) {
    stop("Resolved path leaves data/", area, "/: ", relative_path)
  }
  path
}

sha256_file <- function(path) {
  if (!requireNamespace("digest", quietly = TRUE)) {
    stop("Cannot verify input identity: digest is unavailable. Use an available SHA-256 implementation before loading data.")
  }
  digest::digest(file = path, algo = "sha256", serialize = FALSE)
}

verify_input_sha256 <- function(path, expected) {
  # Bind this run to the exact file inspected when the notebook was prepared.
  if (!is.character(expected) || length(expected) != 1L || is.na(expected) ||
      !grepl("^[0-9a-fA-F]{64}$", expected)) {
    stop("Fill the expected SHA-256 from the inspected input before loading data.")
  }
  actual <- sha256_file(path)
  if (!identical(actual, tolower(expected))) stop("Input changed: identify the new version before loading ", basename(path), ".")
  actual
}

```

## Change for Your Own Data

Use the exact project-relative Data path above. A missing path stops execution;
do not substitute another CSV or use the template/example data. The CSV reader
below is a scaffold: configure dtypes, date parsing, missing codes, and the reader
for the actual stored format. Fill the expected SHA-256 from the exact file
inspected while preparing this notebook; placeholders or a changed file stop
data loading. Documentation stays pending until executed.

```{r}
INPUT_RELATIVE_PATH <- "data/raw/<INPUT_FILE_NAME.csv>"
input_data_file <- project_file(INPUT_RELATIVE_PATH, "raw")
EXPECTED_SHA256 <- "<INSPECTED_INPUT_SHA256>" # Fill from the exact inspected raw file.
```

## Summary

```{r}
input_fingerprint <- verify_input_sha256(input_data_file, EXPECTED_SHA256)
df <- readr::read_csv(input_data_file, show_col_types = FALSE)
# Set col_types/locale/na above for the actual file, especially IDs and dates.
stopifnot(nrow(readr::problems(df)) == 0L)
print(list(data_path = INPUT_RELATIVE_PATH, rows = nrow(df),
           schema = vapply(df, function(x) paste(class(x), collapse = "/"), character(1)),
           sha256 = sha256_file(input_data_file)))
```

### Sample

```{r}
head(df, 10)
```

### Summary Stats

```{r}
summary(df)
```
