---
title: "Statistical Analysis"
author: "<AUTHOR NAME>"
date: "<YYYY-MM-DD>"
---

<!-- Deliver the Rmd in finding/ directly for review; HTML is not required and
is produced only when separately requested. Use the student's requested or
existing filename, or a descriptive basename. Created At and the YAML date
are fixed creation dates. Follow the project-root FINDING-RULES.md for handoff
and external-action scope. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Background

- **Author**: `<AUTHOR NAME>`
- **Created At**: `<YYYY-MM-DD>`
- **Research Motivation and Context (why are we interested in the findings?)：**
- **Main Findings and Takeaways：**
- **Future Direction：**

```{r}
# Load packages here


```

```{r}
# Load input data here and please finish all the data manipulation here.
# Finish this block by printing the first ten observations of the data.
# Note:
# - You may only read data from /data/processed.
#   This means this project's data/processed, not the filesystem root;
#   locate the project portably and document the input source and sample.
# - Files in /data/processed should already be cleaned and prepared for analysis.
# - Beyond simple filtering of observations or generating a small number of variables,
#   further data manipulation is not allowed. If more extensive changes are needed,
#   update the source data instead.
# - State exclusions and missing-value handling; send extensive preparation
#   to data/code/ and write the resulting documented data to data/processed/.
```

```{r}
# Before conducting the analysis, report summary statistics for all variables 
# that will be used in this notebook:
#   - For numeric variables: mean, min, 25th percentile, median, 75th percentile, 
#     max, standard deviation, and number of observations.
#   - For categorical variables: number of observations and the counts/percentages 
#     of the ten most frequent categories.
# Classify variables by meaning (including numeric category codes).
# Include outcomes, predictors, controls, groups, and weights actually used.
# Report numeric effective N and missing N. Categorical percentages use all
# nonmissing observations, not just the top-ten subtotal; report missingness
# separately and state the denominator. Use all categories when fewer than ten.
# Give summary tables titles, readable variable labels, and sample sizes.
# Conclude this block with the complete summary statistics.
```

### The actual analysis starts below
Make the graphs, summary statistics, regression model below.
Make sure you have followed the guidelines as specified in 
[專案資料夾結構、檔案命名與文件規範](https://docs.google.com/document/d/1sl6gEFMdmiGsiNjLe17UmZ30xKxq15U0Mb2B-Jvusxg/edit?tab=t.33iie8ybx7s4).

Use the instructions below for the analyses needed to answer the research question.
Replace this guidance with executed analysis and explanatory text; do not add an
unneeded model or copy example findings.

- **Figures:** Add a title, readable variable names, x/y axis labels, and
  informative legend labels when needed. Avoid overlapping text; address dense
  scatter points with a suitable display. Show 95% confidence intervals for
  estimated quantities such as means. Explain what is plotted, which sample it
  uses, the question, and what the actual figure shows.
- **Tables:** Add a title, sample size, and readable variable labels. For two
  groups, report each group's mean and standard deviation, the mean difference
  (state its direction), and the t-test p-value. Explain the sample, test
  assumptions, findings, and complex or judgment-dependent variable definitions.
- **Regression:** Report the outcome mean on each model's estimation sample and
  N. Default to heteroskedasticity-robust standard errors (e.g., HC1); use
  cluster-robust errors when the design warrants them, naming the cluster
  variable and number of clusters. Identify each categorical variable's omitted
  group. Describe included fixed effects without printing all their coefficients.
  Define significance stars as `* p < .10`, `** p < .05`, `*** p < .01`
  (the instructor's `0.90*`, `0.95**`, `0.99***` notation); p-values may also be
  shown. Explain the specification, sample, standard errors, and variable
  definitions. Use 95% confidence intervals in coefficient plots.

```{r analysis}
# Implement only the graphs, tests, or models required for this question.
# Display actual outputs and add explanatory prose after each relevant output.
# For regression, select the estimation sample before computing its outcome mean;
# compute inference using the stated robust/cluster-robust covariance estimator.
```

Explain the observed results and limitations here, then fill `Main Findings and
Takeaways` from those results. Keep the document understandable without the chat.
If work is unexecuted or only partially executed, state that status and the
specific blocker inside the document; do not invent results.

<!-- Completion: execute the Rmd in a clean R session. knitr::knit() may write
its output and figures to a temporary location for verification; these temporary
files are not additional deliverables. Inspect actual tables and figures for
readable labels and nonoverlapping text, and check that the Rmd's recorded
findings agree with execution results. Deliver the Rmd directly and record its
actual execution status. Produce HTML only when separately requested, never as
a default export or a condition of completion. -->
