---
title: "template-prediction-model"
date: "<YYYY-MM-DD>"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(error = FALSE)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

# Background
- **Author**: `<AUTHOR NAME>`
- **Created At**: `<YYYY-MM-DD>`
- **Path to Training Data：**
- **Path to Testing Data：**
- **Model Specification：**
    - Method：
    - Variables：
    - Tuning Parameters：
    - Optimization Method：
- **Main Findings and Takeaways：**
    - In-sample `<metric>`:
    - Out-sample `<metric>`:
- **Future Direction：**

> Template only — not executed. Replace this note with the actual execution
> status. After confirming the student's format, language, author, and question,
> use the student's requested name, preserve an existing name, or choose a
> descriptive basename. Deliver the `.Rmd` directly for review; HTML is not
> required and is produced only when separately requested. `Created At` and the
> YAML date use the fixed creation date. Follow the project-root
> `FINDING-RULES.md` for execution and presentation.

```{r load-packages}
# Load packages here
```

```{r load-training-data}
# Load the TRAINING data here and please finish all the data manipulation here.
# Finish this block by printing the first ten observations of the data.
# Note:
# - You may only read analysis data from this project's data/processed/.
# - Use portable paths that work from the project root or finding/.
# - Files in /data/processed should already be cleaned and prepared for analysis.
# - Beyond simple filtering of observations or generating a small number of variables,
#   further data manipulation is not allowed. If more extensive changes are needed,
#   update the source data instead.
```

```{r load-testing-data}
# Load the TESTING data here and please finish all the data manipulation here.
# Finish this block by printing the first ten observations of the data.
# Use this project's data/processed/ and the same limited-manipulation rules.
# Preserve the documented split; do not create test labels when unavailable.
```

### Descriptive statistics

Summarize every variable used in the analysis, including the target,
predictors, and applicable derived, filtering, or grouping variables. Treat
numeric-coded categories as categorical when appropriate. Present training
and testing summaries separately; do not use test distributions for model
selection. Explain the sample and variable definitions in the report language.

```{r training-descriptive-statistics}
# TRAINING DATA: produce titled tables with readable variable labels.
# Continuous: mean, min, q25, q50, q75, max, sd, N (#obs, nonmissing).
# Categorical: top ten categories, count, percentage; show all if fewer than ten.
# State total sample size, missing-value treatment, and percentage denominators.
# Replace these comments with code operating on the actual training variables.
```

```{r testing-descriptive-statistics}
# TESTING DATA: produce the same summaries for available analysis variables.
# If the target is absent, summarize available predictors and explain why its
# summary is unavailable. Never synthesize outcomes to complete a table.
# State sample size, missing-value treatment, and percentage denominators.
```

### The actual modeling starts below
For the remaining blocks, make sure you have followed the guidelines as specified in 
[專案資料夾結構、檔案命名與文件規範](https://docs.google.com/document/d/1sl6gEFMdmiGsiNjLe17UmZ30xKxq15U0Mb2B-Jvusxg/edit?tab=t.33iie8ybx7s4).


```{r model-specification}
# Include the model specification here.  Please describe the model by stating, including
# type of method used, the variables included, the hyperparameters, and
# the method of optimization.
# Document split units/sizes, seed, validation strategy, and prediction time.
# For binary tasks, specify the positive class and threshold chosen using
# training/validation data only. Do not tune with testing outcomes/distributions.
```

```{r fit-model}
# Fit using training data. Learn imputation, scaling, encoding, and feature
# selection within training data (and separately within each CV training fold).
# Apply fitted transformations to validation/testing data without refitting.
```

```{r generate-predictions}
# Generate separate training and testing predictions from the fitted model.
# For binary tasks retain continuous positive-class scores for AUC as well as
# thresholded predictions for Recall, Accuracy, F1-Score, and confusion matrices.
```

```{r training-performance}
# Report the performance metrics for training data in this block.
# Continuous target: report MSE AND MAE (RMSE is optional, not a replacement).
# Plot: (1) prediction distribution; (2) predicted versus actual;
# (3) predicted versus prediction error. Define error, e.g. actual - predicted.
# Binary target: report Recall, Accuracy, AUC, F1-Score and a confusion matrix.
# Compute AUC from continuous positive-class scores, never hard class labels.
# State sample size, units, positive class, threshold, and undefined-metric reasons.
# Follow shared figure/table rules and explain the actual findings in prose.
```

```{r testing-performance}
# Report the performance metrics for testing data in this block.
# Use the same required metrics and plots as the training block, labeled TESTING.
# With no true test labels, provide predictions and feasible distribution plots;
# explicitly mark label-dependent metrics/plots unavailable rather than inventing them.
# If an evaluation split has only one class, mark AUC unavailable with a reason;
# explain other undefined metrics (e.g. recall when no positive outcomes exist).
# For multiclass/other tasks, document appropriate extensions and averaging.
# Interpret held-out results separately from training/CV results and backfill
# Main Findings only from actual outputs. Deliver the Rmd with its actual execution status.
```

<!-- Completion: execute the Rmd in a clean R session. knitr::knit() may write
its output and figures to a temporary location for verification; these temporary
files are not additional deliverables. Inspect the actual training/testing
results, tables, and figures for readable labels, nonoverlapping text, and
agreement with the Rmd's takeaways. Deliver the Rmd directly. Produce HTML only
when separately requested, never as a default export or a condition of completion. -->
